---
title: "Unemployment in India During Covid-19"
author: "Jasleen Kaur Wahi"
date: "09/04/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
#The plots drawn below are for before the outbreak of covid-19
```{r}
Unemployment<-read.csv("Unemployment in India.csv")
summary(Unemployment)
library(ggplot2)
ggplot(data=Unemployment,aes(y=Estimated.Unemployment.Rate....,x=ï..Region,col=ï..Region))+geom_point()
ggplot(data=Unemployment,aes(y=Estimated.Unemployment.Rate....,x=ï..Region,col=ï..Region))+geom_point()->lay1
lay1+theme(panel.background = element_rect(fill="lemonchiffon2"))->lay2
lay2+theme(plot.background = element_rect(fill = "lightcoral"))->lay3
lay3+labs(title = "Estimated Unemployment Rate w.r.t Region",x="Region",y="Estimated Unemployment Rate",fill="Region")->lay4
lay4+theme(plot.title = element_text(hjust = 0.5,face = "bold"))

```
Comments: The scatter plot between region w.r.t estimated unemployment rate shows the unemployment rate in different areas of different regions. This plot shows unemployment rate in different areas.

```{r}
ggplot(data=Unemployment,aes(x=Estimated.Unemployment.Rate....))+geom_histogram(bins=100,fill="pink",col="red")
ggplot(data=Unemployment,aes(x=Estimated.Unemployment.Rate....))+geom_histogram(bins=100,fill="pink",col="red")->b1
b1+labs(title = "Estimated Unemployment Rate",x="Estimated Unemployment Rate")->b2
b2+theme(plot.title = element_text(hjust = 0.5,face = "bold"))

```
Comments:The histogram for estimated unemployment rate is right skewed. The unemployment rate is mostly between 0-40% but occassionally it goes till 60-80%.
```{r}
ggplot(data=Unemployment,aes(x=ï..Region,y=Estimated.Unemployment.Rate....,fill=Area))+geom_boxplot()
ggplot(data=Unemployment,aes(x=ï..Region,y=Estimated.Unemployment.Rate....,fill=Area))+geom_boxplot()->obj1
obj1+labs(title="Region w.r.t Estimated Unemployment Rate",x="Region",y="Estimated Unemployment Rate",fill="Area")->obj2
obj2+theme(panel.background = element_rect(fill = "pink"))->obj3
obj3+theme(plot.title = element_text(hjust = 0.5,face = "bold",color = "blue"))->obj4
obj4+theme(plot.background = element_rect(fill = "yellow"))
```
Comments:This boxplot is between different areas(Rural and urban) of different regions and estimated unemployment rate which clear shows the unemployment rate of different regions.

#The plots drawn are for after the outbreak of covid-19

```{r}
Unemployment1 = read.csv("Unemployment_Rate_upto_11_2020.csv")
summary(Unemployment1)
ggplot(data=Unemployment1,aes(y=Estimated.Unemployment.Rate....,x=Region,col=Region))+geom_point()
ggplot(data=Unemployment1,aes(y=Estimated.Unemployment.Rate....,x=Region,col=Region))+geom_point()->la1
la1+theme(panel.background = element_rect(fill="lemonchiffon2"))->la2
la2+theme(plot.background = element_rect(fill = "lightcoral"))->la3
la3+labs(title = "Estimated Unemployment Rate w.r.t Region",x="Region",y="Estimated Unemployment Rate",fill="Region")->la4
la4+theme(plot.title = element_text(hjust = 0.5,face = "bold"))

```
Comments: The scatter plot between region w.r.t estimated unemployment rate shows the unemployment rate in different areas of different regions. This plot shows unemployment rate in different areas.

```{r}
ggplot(data=Unemployment1,aes(x=Estimated.Unemployment.Rate....))+geom_histogram(bins=100,fill="pink",col="red")
ggplot(data=Unemployment1,aes(x=Estimated.Unemployment.Rate....))+geom_histogram(bins=100,fill="pink",col="red")->ba1
ba1+labs(title = "Estimated Unemployment Rate",x="Estimated Unemployment Rate")->ba2
ba2+theme(plot.title = element_text(hjust = 0.5,face = "bold"))

```
Comments:The histogram for estimated unemployment rate is right skewed. The unemployment rate is mostly between 0-30% but occassionally it goes till 40-80%.
